A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-22 tex/body.tex
some edits

The calculus consists of three sets of rules, given in
\figuresname~\ref{fig:cc-rules} to \ref{fig:split-rule}, corresponding to three
phases. The first phase computes the bidirectional closure of $\Ec$. The second
phase makes inferences based on acyclicity (for datatypes) and uniqueness
(for codatatypes).
The third phase performs case distinctions on constructors for
various terms occurring in $\Ec$.
%Following the conventions from~\cite{},
%The derivation rules are given in \relax{guarded assignment form},
%where
%
The rules belonging to a phase have priority over those of the subsequent
phases. Rules are applied until the derivation tree is closed or all leaf nodes
are saturated.

@@

\ourparagraph{Phase 1: Computing the Bidirectional Closure \beforefig(\figurename~\ref{fig:cc-rules}).}
In conjunction with \rn{Refl}, \rn{Sym}, and \rn{Trans}, the \rn{Cong} rule computes the (upward) congruence closure,
whereas the \rn{Inject} and \rn{Clash} rules together compute (downward) unification.
For unification, additional equalities are inferred based on the injectivity of constructors by \rn{Inject},
and failures to unify equated terms are recognized by \rn{Clash}.
The \rn{Conflict} rule recognizes when an equality and its negation both occur in $\Ec$, in which case $\Ec$ has no model.

>>>>

The calculus consists of three sets of rules, given in
\figuresname~\ref{fig:cc-rules} to \ref{fig:split-rule}, corresponding to three
phases. The first phase computes the bidirectional closure of $\Ec$. The second
phase makes inferences based on acyclicity (for datatypes) and uniqueness
(for codatatypes).
The third phase performs case distinctions on constructors for
various terms occurring in $\Ec$.
%Following the conventions from~\cite{},
%The derivation rules are given in \relax{guarded assignment form},
%where
%
The rules belonging to a phase have priority over those of %the
subsequent
phases. The rules are applied until the derivation tree is closed or all leaf nodes
are saturated.

@@

\ourparagraph{Phase 1: Computing the Bidirectional Closure \beforefig(\figurename~\ref{fig:cc-rules}).}
In conjunction with \rn{Refl}, \rn{Sym}, and \rn{Trans}, the \rn{Cong} rule computes the congruence (upward) closure,
whereas the \rn{Inject} and \rn{Clash} rules %together
compute the unification (downward) closure.
For unification, additional equalities are inferred based on the injectivity of constructors by \rn{Inject},
and failures to unify equated terms are recognized by \rn{Clash}.
The \rn{Conflict} rule recognizes when an equality and its negation both occur in $\Ec$, in which case $\Ec$ has no model.
